Distanced-based VOCC analysis

### 2019-05-17 analysis/VOCC/dist-vocc.Rmd
example analysis code using make_vector_data and plot_vocc functions

nd <- rbind(nd_1, nd_3, nd_4, nd_16)
# nd <- nd_4 # for faster test option
nd <- nd %>% dplyr::mutate(shallow = ifelse(depth > 35, 0, 1))
```

@@

Calculate predicted values
```{r}
# m_temp <- readRDS("../VOCC/data/m_temp_post2003.rds")
 m_temp <- readRDS("../VOCC/data/m_temp_allyears.rds")

# can also be filtered to include only year with multiple surveys 
# m_temp <- readRDS("../VOCC/data/m_temp_allpost2003.rds")
# nd <- nd %>% dplyr::filter(year > 2003)
nd <- nd # %>% filter(ssid == 4)

@@

```{r}
# choose the spatial range to build raster on
predicted1 <- predictions %>% filter(ssid == 1) 
predicted3 <- predictions %>% filter(ssid == 3) 
predicted4 <- predictions %>% filter(ssid == 4) 
predicted16 <- predictions %>% filter(ssid == 16) 
predicted1n3 <- predictions %>% filter(ssid != 16) %>% filter(ssid != 4) %>% filter(year > 2004)

@@

```{r}

# scale_fac = 2 means that the raster is reprojected to 2 X original grid (2 km)
rbrick <- make_raster_brick(predicted3, scale_fac = 2)
saveRDS(rbrick, file = "analysis/data/rbrick-temp-hs.rds")

# scale_fac = 2 means that the raster is reprojected to 2 X original grid (2 km)
rbrick <- make_raster_brick(predicted1, scale_fac = 2)
saveRDS(rbrick, file = "analysis/data/rbrick-temp-qcs.rds")

# scale_fac = 2 means that the raster is reprojected to 2 X original grid (2 km)
rbrick <- make_raster_brick(predicted4, scale_fac = 2)
saveRDS(rbrick, file = "analysis/data/rbrick-temp-wcvi.rds")

# scale_fac = 2 means that the raster is reprojected to 2 X original grid (2 km)
rbrick <- make_raster_brick(predicted16, scale_fac = 2)
saveRDS(rbrick, file = "analysis/data/rbrick-temp-wchg.rds")

rbrick <- make_raster_brick(predicted1n3, scale_fac = 2)
saveRDS(rbrick, file = "analysis/data/rbrick-temp-hs-qcs.rds")

```

```{r}
make_vector_data <- function(climate_data, 
  ssid = NULL,
  start_year = NULL,
  input_cell_size = 2, 
  scale_fac = 2,
  delta_t_total = 10,
  delta_t_step = 2,
  time_slices = 7, 
  indices = c(1, 1, 2, 2, 2, 3, 3),
  thresholds = c(0.75)
  ) {

if (!is.null(ssid)) climate_data <- climate_data[climate_data$ssid %in% ssid, ]
if (!is.null(start_year)) climate_data <- climate_data %>% dplyr::filter(year >= start_year)

#if (!identical(time_slices, length(indices)))
length_indices <- length(indices)
if(!isTRUE(time_slices==length_indices))
      stop("Must have an indice assigned to each time slice,",
      "therefore length('indices') must equal 'time_slices'.",
      call. = FALSE)

#FIXME: need way of determining how many variables(in separate dataframes) are in dataset  
#if (!is.list(climate_data)) {
# if (length(thresholds) > 1)
#       stop("If multiple climate variables (and corresponding thresholds),", 
#         "data must be in list form.", call. = FALSE)

rbrick <- make_raster_brick(climate_data, scale_fac = scale_fac)
mnraster_brick <- raster::stackApply(rbrick, indices = indices, fun = mean)
start_raster <- mnraster_brick[[1]]
end_raster <- mnraster_brick[[3]]

# make sparate named lists containing climate rasters or dataframes
# data with just one climate variable
start_data <- list(var_1 = start_raster)
end_data <- list(var_1 = end_raster)

# } else {
#     if (!identical(length(climate_data), length(thresholds)))
#       stop("Must have a 'thresholds' value for each climate variable", call. = FALSE)
# rbrick <- list()
# for (i in seq_len(climate_data)) {
#   
# rbrick[[i]] <- make_raster_brick(climate_data[[i]], scale_fac = scale_fac)
# mnraster_brick <- raster::stackApply(rbrick[[i]], indices = indices, fun = mean)
# 
# start_raster <- mnraster_brick[[1]]
# end_raster <- mnraster_brick[[3]]
# var <- list(start_raster = start_raster, end_raster = end_raster)
# }

# start_data <- list(var = var$start_raster[[i]])
# end_data <- list(var = var$end_raster[[i]])
#}

out <- dist_based_vocc(
  start_data = start_data,
  end_data = end_data,
  x = "x",
  y = "y",
  variable_names = c("index_1"), # what the layer within each element is called
  thresholds = thresholds,
  cell_size =  input_cell_size*scale_fac,
  delta_t = delta_t_total,
  raster = TRUE
  )

# FIXME: need to change function to deal with different time steps within a brick
slopedat <-  calcslope(rbrick, delta_t_step = delta_t_step) # vocc::calcslope for comparison
out <- left_join(out, slopedat, by = c("x", "y")) %>% select(-icell)
out$C_per_decade <- out$slope * 10
out$km_per_decade <- (out$distance/delta_t_total)*10 
out
}

```

```{r}
out <- make_vector_data (predictions, 
  ssid = c(1, 3),
  start_year = 2005,
  input_cell_size = 2, 
  scale_fac = 2,
  delta_t_total = 10,
  delta_t_step = 2,
  time_slices = 7,
  indices = c(1, 1, 2, 2, 2, 3, 3),
  thresholds = c(0.75)
  )
glimpse(out)
```

>>>>

nd <- rbind(nd_1, nd_3, nd_4, nd_16)
nd <- nd %>% dplyr::mutate(shallow = ifelse(depth > 35, 0, 1))
```

@@

Calculate predicted values
```{r}
m_temp <- readRDS("../VOCC/data/m_temp_allyears.rds")

# can also be filtered to exclude certain years
# m_temp <- readRDS("../VOCC/data/m_temp_allpost2003.rds")
# nd <- nd %>% dplyr::filter(year > 2003)

@@

Explore subsets ot the spatial range 
```{r eval=FALSE}
predicted1 <- predictions %>% filter(ssid == 1) 
predicted3 <- predictions %>% filter(ssid == 3) 
predicted4 <- predictions %>% filter(ssid == 4) 
predicted16 <- predictions %>% filter(ssid == 16) 
predicted1n3 <- predictions %>% filter(ssid != 16) %>% filter(ssid != 4) %>% filter(year > 2004)

@@

```{r}
out <- make_vector_data (predictions, 
  ssid = c(1),
  start_year = 2005,
  input_cell_size = 2, 
  scale_fac = 2,
  delta_t_total = 10,
  delta_t_step = 2,
  time_steps = 7,
  indices = c(1, 1, 1, 2, 3, 3, 3),
  thresholds = c(0.5) # vector of plus/minus threshold(s) to define climate match.
  )
glimpse(out)
```
